Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-05-29 PaperLatex/paper.tex
minor fixes

The software has been implemented in \texttt{MATLAB} due to its ease-of-use and popularity among neuroscientists. \texttt{cpplab} provides a powerful backend for specifying and integrating models without relying on the significantly slower and limiting \texttt{MATLAB codegen}. While automated \texttt{C++} transpiling from \texttt{MATLAB} using the proprietary \texttt{coder} can drastically improve performance over loops through strong typing and memory pre-allocation, supervenience of \texttt{MATLAB} over \texttt{C++} prevents efficient use of low-level features, such as passing by reference and object-oriented programming.   Minimal experience with \texttt{MATLAB} is required to use \texttt{xolotl}, and all equations and integration methods are provided transparently to the end user. No string parsing of equations is required \autocite{sherfeyDynaSimMATLABToolbox2018, stimbergBrianSecondComing2013, stimbergEquationorientedSpecificationNeural2014}.

@@

Simulations can be run in 'open-loop' mode where each simulation begins by resetting all dynamical variables to their initial conditions at instantiation, or 'closed-loop' mode which begins simulation with the current network state.

@@

The code to generate all figures can be found in the \texttt{xolotl-paper} repository (\url{https://github.com/marderlab/xolotl-paper}). "xolotl" can be downloaded from its repository (\url{https://github.com/marderlab/xolotl}).

>>>>

The software has been implemented in \texttt{MATLAB} due to its ease-of-use and popularity among neuroscientists. \texttt{cpplab} provides a powerful backend for specifying and integrating models without relying on the significantly slower and limiting \texttt{MATLAB codegen}. While automated \texttt{C++} transpiling from \texttt{MATLAB} using the proprietary \texttt{codegen} can drastically improve performance over loops through strong typing and memory pre-allocation, supervenience of \texttt{MATLAB} over \texttt{C++} prevents efficient use of low-level features, such as passing by reference and object-oriented programming.   Minimal experience with \texttt{MATLAB} is required to use \texttt{xolotl}, and all equations and integration methods are provided transparently to the end user. No string parsing of equations is required \autocite{sherfeyDynaSimMATLABToolbox2018, stimbergBrianSecondComing2013, stimbergEquationorientedSpecificationNeural2014}.

@@

Simulations can be run in 'closed-loop' mode where each simulation begins by resetting all dynamical variables to their initial conditions at instantiation, or 'open-loop' mode which begins simulation with the current network state.

@@

The code to generate all figures is available at (\url{https://github.com/marderlab/xolotl-paper}). "xolotl" is frely available at (\url{https://github.com/marderlab/xolotl}).
